\documentclass{article}

\usepackage[margin=1.5in]{geometry}
\usepackage[dvipsnames]{xcolor}

\title{Understanding Innovation Marketing}
\author{Anurag Sahu, 19120016}
\date{\today}

\begin{document}
\maketitle


\section{Abstract}

This study aims to investigate the development of ‘innovation marketing’ defined as the 
implementation of new marketing practices involving significant changes in the design,
distribution, promotion or pricing of a product or service.
Innovation and marketing have frequently been viewed as the different sides of the coin. These two terms are like an 
inseparable couple because neither marketing nor innovation can achieve success without each other's help.
It plays a major role in managing and upscaling any business.
The job of innovation in marketing is to investigate new business sectors to build deals and productivity.
However, if innovation marketing is not enforced and pursued with
priority, there are many risks and dangers that must be avoided in an innovation project.Many startups and
existing giants collapsed due to this negligence. This review
will cover techniques related to innovation marketing such as social media marketing,
word of mouth marketing, etc. In this paper, we will also discuss the failure of kodak due
to their unwillingness to innovate and how IKEA used this concept of innovation
marketing for their growth.

\section{Introduction}

Innovation marketing is the combination
of two of the important words:
“Innovation” and “marketing” . As the
famed expert in management, Peter
Drucker said that marketing and
innovation are the basic functions to
upscale any business. This is because,
just as marketing requires innovation for
product success, innovation requires
marketing.
To put it another way, innovation is the
process of turning an invention idea into a
product or service that adds value or that
customers will pay for it. Marketing, on the other hand, is the process through which manufacturers communicate to consumers the qualities and benefits of their products
and services (Lead Innovation).
The strong focus on customers in innovation marketing generates practical insights,
which is why it is particularly effective for new technology enterprises. A personalized
marketing plan can be used to extend the product's lifespan by attentively listening to
comments and keeping track of what's going on in the industry. When considering the
complexity of technology products and services, a customer-centric approach is bound
to have the largest market adoption.

\section{Importance of Innovation Marketing}
The simple depiction of the task and role of innovation marketing clarifies how
significant the capacity in the innovation cycle is. Innovation marketing assumes a part
in all stages and consequently guarantees client and market direction, a significant
switch to stay away from the failure of
an innovation.
Notwithstanding, on the off chance that
innovation marketing isn't authorized
and sought after with need, there are
many dangers and risks that should be
kept away from in an innovation project.

\begin{itemize}
\item Assuming that there is an absence
of data about the market, clients,
users and their necessities or then
again in the event that they are
insufficient (e. g. not agent or
deficient), wrong choices are made
as to the item or the objective
market, which can drive an
undertaking off course and, accordingly, drive it to the divider. For instance, the item
is lost, some unacceptable objective market is picked or superfluous necessities
are tended to.

\item The product does not sell. This doesn't be guaranteed to imply that the item is
terrible. There are unremarkable items that are showcased impeccably and are
consequently more fruitful than those that are best in class yet are severely
advertised. Marketing is subsequently a significant achievement factor, both inside
and remotely.
\end{itemize}
These two focuses clarify that innovation marketing is a significant switch for the
outcome of development. Around 60 to 80 percent of new items fall flat and a
significant number of the reasons depend on an absence of client direction and
marketing. That is the reason innovation managers and project managers need to
manage innovation marketing and work intimately with advertising and deals.

\section{Why marketers use Innovative Marketing}
The job of innovation in marketing is to investigate new business sectors to build deals
and productivity. Innovation marketing believes in the dynamics of the business world
that are changing on a regular basis and so as the marketing strategies as well.
Marketers know that conventional marketing techniques are not effective anymore and
the businesses are surrounded by advanced technology. Innovative methodologies in
advertising permit marketers to follow the presentation and modify the methodologies
to better cater the clients' requirements.

\section{Innovation Marketing VS. Innovative Marketing -}
You might think there's no difference between these two terms at first glance. But don't
be deceived by tiny spelling changes! How about we view it in more detail.
The promotion of a novel product or service is known as innovation marketing. In this
context, innovation refers to a new product or service as well as the method of
launching, bringing it to market, and growing and scaling it.
This is distinct from innovative marketing, which is the use of a novel marketing strategy
that has never been used before.
To summarize, innovation marketing is the act of marketing new products/services,
while innovative marketing is the act of marketing a new marketing strategy.

\section{Failure to launch}

According to Fortune, nine out of ten startups fail. Additionally, each year more than
30,000 new consumer products are launched with over 80% failing (Harvard Business
Review). Here are some of the key reasons why:

\begin{itemize}
\item Customer orientation: There is an absence of foundation examination and data
available, industry, clients, clients, and their necessities.

\item Ineffective strategies: marketing direction or procedures that don't fit the
organization, industry, item, administration and timing of the market.

\item Foresight: Assuming an organization is reluctant to change and advance and
their true capacity becomes restricted or old.

\end{itemize}
With these high failure insights, innovation marketing is the method for beating the
mass reception boundary. By zeroing in on the informing, situating, crowd ID and the
de-jargoning of the specialized parts of new items/administrations will place the item or
administration in a good position. Also, without a reasonable development plan, there
will be stagnation of client reception.

\section{Innovative Marketing Techniques}

Marketing Managers require endless marketing efforts to increase brand awareness
and visibility in such a way that has a positive impact on consumer’s mind while trying
to squeeze the marketing budgets.On the off chance that they can't convey they can
lose a share of the market to another participant.
Following are some of the innovative marketing procedures that can assist marketers
with drawing in more clients inside restricted showcasing spending plans.

Word of Mouth Marketing

This is maybe the most remarkable kind of promotion as it is finished by blissful and
fulfilled clients. The fundamental goal of the organization is to convey a one of a kind
client experience in such a manner to surpass clients' assumptions. A fulfilled client will
continuously remain faithful to your image. Remember to plan your clients' excursion
and make them stunned each time they associate with your image.
Social Media Marketing

In the present world, social platforms have democratized both marketing and customer
engagements. This probably means that the person who has the best ideas and
techniques that leads to client engagements will win a big market share rather than the
one who spends a huge budget on advertising. Based upon the company’s target
market and demographics, social media platforms are the resources which can bridge
the gaps between product and customer. However, customers are kings and they have
the luxury to switch to a new entrant or existing quality brand. Here marketers are
required to come up with an authentic and innovative idea to resolve customer
problems effectively and efficiently.
Retain Your Existing Customers

Keep in mind, if you acquire new customers it is seven times more expensive than
retaining the existing customers. You should guarantee that your current clients are held
until the end of time. Ascertain client lifetime worth to an organization and afterward
put more endeavors to hold them. Your whole organization ought to zero in on client
assistance assuming you lose even one; continue to dig until you track down the
reasons.

Brand Repositioning

When Hunter Hayes says "Now is the right time to reset, reevaluate, and reposition". At
the point when your business is struggling, it is the perfect opportunity for the business
to accept it as a test and reevaluate your methodology. Lead a swot investigation to
figure out your business assets and shortcomings. What is your company's USP or
upper hand over your rivals? Once you are able to answer these questions, do what you
do better and dig deeper to fine tune how you can better serve your customers.

\section{A Small brief on the failure of KODAK}

Kodak is one organization that accomplished disappointment because of a reluctance
to enhance. Steve Sasson, the organization's specialist, designed the main advanced
camera in 1975. Notwithstanding, on the grounds that the camera was filmless and
most of Kodak's income at the time was to sell film, Kodak's administration excused it
totally (New York Times 2015). The organization might have been at the bleeding edge
of advancement, yet rather was totally upset by the market as Kodak neglected to adjust
to another commercial center and new purchaser perspectives and declared financial
insolvency in 2012.
The marketing group at Kodak
attempted to persuade the managers
about the change required in the
organization's center standards to
make progress. However, Kodak's
administration board of trustees kept
on staying with its obsolete thought of
depending on film cameras and
asserted the columnist who said the
proclamation in the magazine didn't
have the information to back his
suggestion.
Kodak neglected to understand that its methodology which was compelling at one point
was currently denying it progress. Quickly changing innovation and market needs
discredited the technique. Kodak put its assets in procuring many little organizations,
exhausting the cash it might have used to advance the deals of computerized cameras.
Whenever Kodak at last got it and began the deals and the creation of computerized
cameras, it was past the point of no return. Many enormous organizations had proactively set up a good foundation for themselves in the market by then and Kodak
couldn't stay up with the big cheeses.

\section{ A Small brief on the success of IKEA}

IKEA began in 1943 as a mail-request deals organization and has developed into a
partnership that traverses 52 nations. It's had the option to remain applicable for such a
long time on account of innovation marketing. In 2013, the organization sent off the
Catalog application, which gives individuals admittance to the whole store stock. It
likewise incorporates an expanded reality that allows individuals to perceive how pieces
examine their own homes before buying. The organization doesn't simply improve with
outward channels, possibly it gives development in stores as well. On location, IKEA has
free looking after children play regions for kids, in-store eateries, and family
participation plans.
The people who visit an IKEA store can anticipate various innovations intended to make
phenomenal shopping encounters.
IKEA also makes efforts to cater for customers’ post-purchase needs, even though it
may have no direct revenue return for the brand. In previous years, for example, they
introduced a platform that helped customers sell their second-hand furniture, even
going as far as helping users take photos and opening up the brand's Facebook page to
go about as an internet based commercial center. Initiatives have been resolutely centered around further developing the total purchasing
encounters of their clients, without falling into laid out ideal models or normal cycles.
While many brands value that client experience is vital to an effective system, IKEA has
figured out how to execute on a degree of detail where various others miss the mark.

\section{ Conclusion}

Innovation marketing works in the front finish of the advancement interaction to
investigate market possibilities and client needs, gets criticism from the client in the
improvement cycle and markets the item at the back finish of the cycle. Innovation
marketing thus guarantees that the new items and administrations are outfitted to the
market and clients. This is one of the greatest achievement factors in advancing the
board to increment income, open doors and wipe out flops and superfluous waste.
Innovation marketing techniques helped many organizations like IKEA to expand their
business. In this paper, We discussed the failure of kodak due to their unwillingness to
innovate and how IKEA used this concept of innovation marketing for their growth.

\section{Reference}
\begin{itemize}
\item https://www.lead-innovation.com/english-blog/innovation-marketing
\item  https://www.researchgate.net/publication/342061122_Marketing_innovation_a_
systematic_review
\item https://www.forestlyn.com/blog/2019/10/6/innovation-marketing-the-successsecret-of-emerging-tech
\item  https://stats.oecd.org/glossary/detail.asp?ID=6871
\item  https://www.marketingtutor.net/innovative-marketing/
\item  https://www.linkdex.com/en-gb/inked/innovative-marketing-strategies-example
s/
\item  https://www.copypress.com/kb/content-marketing/innovative-marketing-what-i
t-is-and-methods-to-try/
\end{itemize}
\end{document}
